Conceptualizing open health data platforms for low- and middle income countries

### 2024-02-14 paper-data-platforms.qmd
wip

---
title: "Conceptualizing open health data platforms for low- and middle income countries"
format:
  # docx
  # typst:
  #   columns: 1
  elsevier-pdf:
    keep-tex: true
    journal:
      cite-style: authoryear
author:
  - name: Daniel Kapitan
    affiliations:
      - name: PharmAccess Foundation
        city: Amsterdam
        country: the Netherlands
      - name: Eindhoven University of Technology
        city: Eindhoven
        country: the Netherlands
    orcid: 0000-0001-8979-9194
    email: daniel@kapitan.net
  - name: Femke Heddema
    affiliations:
      - name: PharmAccess Foundation
        city: Amsterdam
        country: the Netherlands
  - name: Julie Fleischer
    affiliations:
      - name: PharmAccess Foundation
        city: Amsterdam
        country: the Netherlands
  - name: Chris Ihure
    affiliations:
      - name: PharmAccess Kenya
        city: Nairobi
        country: Kenya
  - name: Antragama Abbas
    affiliations:
      - name: Delft University of Technology
        city: Delft
        country: the Netherlands
  - name: Steven Wanyee
    affiliations:
      - name: IntelliSOFT
        city: Nairobi
        country: Kenya
  - name: XXX
    affiliations:
      - name: ONA
        city: Nairobi
        country: Kenya
  - name: John Grimes
    affiliations:
      - name: Australian e-Health Research Centre
        city: Brisbane
        country: Australia
  - name: Mark van der Graaf
    affiliations:
      - name: PharmAccess Foundation
        city: Amsterdam
        country: the Netherlands
  - name: Mark de Reuver
    affiliations:
      - name: Delft University of Technology
        city: Delft
        country: the Netherlands

>>>>

---
title: "Conceptualizing open health data platforms for low- and middle income countries"
format:
  # docx
  # typst:
  #   columns: 1
  elsevier-pdf:
    keep-tex: true
    journal:
      name: JIMR
      cite-style: authoryear
author:
  - name: Daniel Kapitan
    affiliations:
      - name: PharmAccess Foundation
        city: Amsterdam
        country: the Netherlands
      - name: Eindhoven University of Technology
        city: Eindhoven
        country: the Netherlands
    orcid: 0000-0001-8979-9194
    email: daniel@kapitan.net
  - name: Femke Heddema
    affiliations:
      - name: PharmAccess Foundation
        city: Amsterdam
        country: the Netherlands
  - name: Julie Fleischer
    affiliations:
      - name: PharmAccess Foundation
        city: Amsterdam
        country: the Netherlands
  - name: Chris Ihure
    affiliations:
      - name: PharmAccess Kenya
        city: Nairobi
        country: Kenya
  - name: Antragama Abbas
    affiliations:
      - name: Delft University of Technology
        city: Delft
        country: the Netherlands
  - name: Steven Wanyee
    affiliations:
      - name: IntelliSOFT
        city: Nairobi
        country: Kenya
  - name: XXX
    affiliations:
      - name: ONA
        city: Nairobi
        country: Kenya
  - name: John Grimes
    affiliations:
      - name: Australian e-Health Research Centre
        city: Brisbane
        country: Australia
  - name: Mark van der Graaf
    affiliations:
      - name: PharmAccess Foundation
        city: Amsterdam
        country: the Netherlands
  - name: Mark de Reuver
    affiliations:
      - name: Delft University of Technology
        city: Delft
        country: the Netherlands
